---
title: "How the type of ball changes defense in volleyball"
subtitle: "Through the example of the Korean Volleyball League (KOVO)"
author: "Hillary Lee"
date: "1/16/2022"
output: html_document
---

## Introduction and Data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.width = 8, fig.height = 5)
```

```{r library}
library(tidyverse)
library(stringr)
library(robotstxt)
library(rvest)
library(httr)
library(xml2)
```

The Korean volleyball league uses its own official game ball made by 'Star',
which is different from the Mikasa that is used in most FIVB-regulated games.

'New Champion VB215-34' was used from 2005 until the 2009-10 season, when it was 
changed to 'Grand Champion VB225-34'. According to the Korean Volleyball 
Federation, "elasticity (of the ball) was reinforced...by mixing natural rubber 
and synthetic rubber".

I wanted to quantify how elasticity changed by looking at how it affected player
statistics in passing/reception, serving, and digging.

## Methodology

I will use web scraping to collect data from [KOVO](https://www.kovo.co.kr/).

I collected four data sets:
- Reception from season 2005 to 2009-10.
- Reception from season 2009 to 2020-21.
- Reception from season 2009-10.
- Reception from season 2010-11.

```{r data}
url <- "https://www.kovo.co.kr/stats/42001_team-totalrecord.asp?s_part=2&spart=&s_season=001&s_pr=201%7C1&e_season=006&e_pr=203%7C1&part=r"

reception_0510 <- read_html(url) %>% 
  html_nodes(css = "table") %>% 
  html_table()

reception_0510[[1]] %>% 
  as_tibble()

url <- "https://www.kovo.co.kr/stats/42001_team-totalrecord.asp?s_part=2&spart=&s_season=006&s_pr=201%7C1&e_season=006&e_pr=203%7C1&part=r"

reception_0910 <- read_html(url) %>% 
  html_nodes(css = "table") %>% 
  html_table()

reception_0910[[1]] %>% 
  as_tibble()

url <- "https://www.kovo.co.kr/stats/42001_team-totalrecord.asp?s_part=2&spart=&s_season=007&s_pr=201%7C1&e_season=007&e_pr=203%7C1&part=r"

reception_1011 <- read_html(url) %>% 
  html_nodes(css = "table") %>% 
  html_table()

reception_1011[[1]] %>% 
  as_tibble()

url <- "https://www.kovo.co.kr/stats/42001_team-totalrecord.asp?s_part=2&spart=&s_season=007&s_pr=201%7C1&e_season=017&e_pr=204%7C1&part=r"

reception_1021 <- read_html(url) %>% 
  html_nodes(css = "table") %>% 
  html_table()

reception_1021[[1]] %>% 
  as_tibble()
```

The last column (reception efficiency, 리시브효율) was calculated incorrectly 
because of a change in statistical calculation method on the website, so I 
deleted and recalculated it.

## Data Analysis

## Results

## Discussion

## References

- [Naver Sports Article: V-League changes official game ball](https://sports.news.naver.com/news?oid=109&aid=0002125184)

