---
title: "How the type of ball changes defense in volleyball"
subtitle: "Through the example of the Korean Volleyball League (KOVO)"
author: "Hillary Lee"
date: "1/16/2022"
output: html_document
---

## Introduction and Data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library}
library(tidyverse)
library(stringr)
library(robotstxt)
library(rvest)
library(httr)
```

The Korean volleyball league uses its own official game ball made by 'Star',
which is different from the Mikasa that is used in most FIVB-regulated games.

'New Champion VB215-34' was used from 2005 until the 2009-10 season, when it was 
changed to 'Grand Champion VB225-34'. According to the Korean Volleyball 
Federation, "elasticity (of the ball) was reinforced...by mixing natural rubber 
and synthetic rubber".

I wanted to quantify how elasticity changed by looking at how it affected player
statistics in passing/reception, serving, and digging.

## Methodology

I will use web scraping to collect data from [KOVO](https://www.kovo.co.kr/).



## Data Analysis

## Results

## Discussion

## References

- [Naver Sports Article: V-League changes official game ball](https://sports.news.naver.com/news?oid=109&aid=0002125184)

